Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-01 robdml.tex
tex

\noindent\textbf{III. Intra-Class Structure.}

>>>>

\noindent\textbf{III. Intra-Class Structure.}
%
Although independent to HM, ACT is incompatible with $L_\text{ICS}$ as it does
not create an adversarial anchor.
%
Thus, we validate this loss term with HM.
%
As shown in \cref{tab:ics} and \cref{fig:ics}, $L_\text{ICS}$ consistently
leads to a higher efficiency in gaining robustness, while retaining a
good trade-off between ERS and R@1.
